### 2019-04-29 monograph/thesis/chapters/introduction.tex
Deprecated thee predefined \lang tags added to introduction.tex
and monograph/thesis/chapters/motivation.tex

\lang{%
    Beforehand due the scope limitation for a Graduation Thesis,
    we should only think about a basic, simple,
    and yet reusable core of features.
}{%

}

\begin{enumerate}
    \item
    \lang{%
        A Software Product with a great Object Orientation and possibilities of extension of features,
        decent research on the state of the art.
    }{%

    }
    \item
    \lang{%
        Ranking all code formatting classes (beautifying) applicable.
        Including a study on what does is source beautifying,
        how to do such and why.
    }{%

    }
    \item
    \lang{%
        Establish relationships between good programming practices and efficiency in programming,
        in addition to a new tool to support programmers in order to automate the long and diverse
        programming process in teams of developers with different programming `best practices'.
    }{%

    }
    \item
    \lang{%
        Define, determine and classify which one are good programming practices and
        perform an in\hyp{}depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    }{%

    }
    \item
    \lang{%
        The definition of a flow pattern of development allowing teams of
        developers with different programming best practices,
        to work without intervene with each other up to start wars of `best good practices'.
    }{%

    }
    \item
    \lang{%
        Discourse on the variety of existing tools for the support of good programming practices,
        with a comparative analysis between them,
        determining their weaknesses and strengths.
    }{%

    }
\end{enumerate}

@@

\lang{%
    Propose a unique tool that allowing several and distinct
    programming `best practices' being implemented in several programming
    languages, which can be configured and set accordingly to their wishes,
    from a single software working well behaved across all programming languages.
}{%

}

\lang{%
    Moreover, explain the differences for other softwares and the benefits
    of a unique tool, instead of several heavily different ones.
}{%

}

\lang{%
    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:
}{%

}

\begin{enumerate}[leftmargin=*]
    \item
    \lang{%
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}
    }{%

    }
    \item
    \lang{%
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.
    }{%

    }
    \item
    \lang{%
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}
    }{%

    }
    \item
    \lang{%
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
    }{%

    }
\end{enumerate}

\lang{%
    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.
}{%

}

>>>>

    Beforehand due the scope limitation for a Graduation Thesis,
    we should only think about a basic, simple,
    and yet reusable core of features.

\begin{enumerate}
    \item
        A Software Product with a great Object Orientation and possibilities of extension of features,
        decent research on the state of the art.
    \item
        Ranking all code formatting classes (beautifying) applicable.
        Including a study on what does is source beautifying,
        how to do such and why.
    \item
        Establish relationships between good programming practices and efficiency in programming,
        in addition to a new tool to support programmers in order to automate the long and diverse
        programming process in teams of developers with different programming `best practices'.
    \item
        Define, determine and classify which one are good programming practices and
        perform an in\hyp{}depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    \item
        The definition of a flow pattern of development allowing teams of
        developers with different programming best practices,
        to work without intervene with each other up to start wars of `best good practices'.
    \item
        Discourse on the variety of existing tools for the support of good programming practices,
        with a comparative analysis between them,
        determining their weaknesses and strengths.
\end{enumerate}

@@

    Propose a unique tool that allowing several and distinct
    programming `best practices' being implemented in several programming
    languages, which can be configured and set accordingly to their wishes,
    from a single software working well behaved across all programming languages.

    Moreover, explain the differences for other softwares and the benefits
    of a unique tool, instead of several heavily different ones.

    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:

\begin{enumerate}[leftmargin=*]
    \item
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}
    \item
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.
    \item
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}
    \item
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
\end{enumerate}

    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.
